A Comparison of Different GANs for Generating Handwritten Digits on MNIST

### 2020-04-18 paper.tex
Added quality data table.

>>>>

After running all three architectures for 200 epochs, the training metrics indicated that they all were hitting max performance and that more training would be not much more beneficial. We took the last ten sample outputs from each GAN architecture and asked a random participant to rate the hand written digits on a scale of 1-10, the results are shown in table \ref{tab:quality}. As you can see, the DGGAN outperforms the other two architectures by a large margin.

\begin{table}[]
\caption{\label{tab:quality}This table represents the quality metrics we measured from a random participant. }
\begin{tabular}{lll}
\hline
\multicolumn{1}{|l|}{GAN} & \multicolumn{1}{l|}{WGAN} & \multicolumn{1}{l|}{DCGAN} \\ \hline
\multicolumn{1}{|l|}{7}   & \multicolumn{1}{l|}{7}    & \multicolumn{1}{l|}{10}    \\
\multicolumn{1}{|l|}{6}   & \multicolumn{1}{l|}{8}    & \multicolumn{1}{l|}{10}    \\
\multicolumn{1}{|l|}{7}   & \multicolumn{1}{l|}{7}    & \multicolumn{1}{l|}{10}    \\
\multicolumn{1}{|l|}{6}   & \multicolumn{1}{l|}{7}    & \multicolumn{1}{l|}{10}    \\
\multicolumn{1}{|l|}{5}   & \multicolumn{1}{l|}{7}    & \multicolumn{1}{l|}{10}    \\
\multicolumn{1}{|l|}{4}   & \multicolumn{1}{l|}{8}    & \multicolumn{1}{l|}{10}    \\ \hline
                          &                           &                           
\end{tabular}
\end{table}
